Equipo 7

### 2021-05-07 final/script.Rmd
Update script.Rmd

library(readxl)
library(readr)
library(stargazer)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(Jmisc)
library(stringi)

@@

>>>>

library(readxl)
library(readr)
library(stargazer)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(stringi)
library(rdrobust)
library(rdd)
library(stats)

@@

## Modelo

```{r, results='asis'}

attach(data)
#Comprobamos si hay discontinuidad en nuestro Score

DCdensity(cambio_internet,plot=TRUE)

```{r, results='asis'}

# RDPLOT

out<- rdplot(cambio_mat,cambio_internet, nbins=c(20,20),binselect = "es",y.lim=c(0,+80))
line

out<- rdplot(cambio_esp,cambio_internet, nbins=c(20,20),binselect = "es",y.lim=c(0,+80))
line
```

```{r, results='asis'}
#Plot ..
plot(cambio_internet,cambio_mat)

y.loess <- loess(cambio_mat~cambio_internet,span=.8,
                 data.frame(x=cambio_internet,y=cambio_mat))

y.predict<- predict(y.loess,data.frame(x=cambio_internet))

lines(cambio_internet,y.predict)
